### 2020-03-16 report/04-productivity.Rmd
Compute total biomass and richness by sampled area

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(temporal_community_metrics, synchrony, dir = data_common)
```

```{r prod-dist, fig.cap = "Median community biomass by station"}
biomass_prod_station <- temporal_community_metrics %>%
  select(station, biomass_med, richness_med) %>%
  rename(biomass = biomass_med)

plot_biomass_dist <- ggplot(biomass_prod_station, aes(x = biomass)) +
  geom_histogram() +
  labs(
    x = "Median of biomass (g)",
    y = "# of stations"
  )
plot_biomass_dist
```

@@

>>>>

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
temporal_network_metrics_classes <- temporal_network_metrics
myload(temporal_network_metrics, dir = dest_dir)
myload(community_metrics, dir = data_common)
myload(temporal_community_metrics, synchrony, dir = data_common)
```

```{r prod-dist, fig.cap = "Median community biomass by station"}
biomass_prod_station <- temporal_community_metrics %>%
  select(station, biomass_med, bm_std_med, richness_med, rich_std_med) %>%
  rename(biomass = biomass_med)

plot_biomass_dist <- ggplot(biomass_prod_station, aes(x = biomass)) +
  geom_histogram() +
  labs(
    x = "Median of biomass (g)",
    y = "# of stations"
  )
plot_biomass_dist

plot_biomass_std_dist <- ggplot(biomass_prod_station, aes(x = bm_std_med)) +
  geom_histogram() +
  labs(
    x = "Median of standardized biomass (g/m2)",
    y = "# of stations"
  )
plot_biomass_std_dist
```

@@

### Biomass richness

```{r}
# Raw biomass
raw_bm_rich <- biomass_prod_station %>% 
  select(station, biomass, richness_med) %>%
  rename(richness = richness_med) %>%
  mutate(type = "raw")
std_bm_rich <- biomass_prod_station %>% 
  select(station, bm_std_med, rich_std_med) %>%
  rename(richness = rich_std_med, biomass = bm_std_med) %>%
  mutate(type = "std")

p_bm_rich_raw_std <- map(list(raw_bm_rich, std_bm_rich), function (x) {

  if (unique(x$type) == "raw") {
    x_lab <- paste0("Median richness")
    y_lab <- paste0("Median biomass (g)")
  } else {
    x_lab <- paste0("Median standardized richness (m2^-1)")
    y_lab <- paste0("Median standardized biomass (g/m2)")
  }

  x %>%
  ggplot(aes(x = log10(richness), y = log10(biomass))) +
  geom_point() +
  labs(x = x_lab, y = y_lab)
  })
plot_grid(plotlist = p_bm_rich_raw_std)
```
